A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Electron Beam Dynamics

### 2019-01-31 paper/submission/ZW10157-response-1.tex
finished adding in Linda's edits

\documentclass{article}
\usepackage{latexsym}
\usepackage{color}
\setlength{\parskip}{3mm}
\setlength{\parindent}{0pt}
\usepackage[margin=1in]{geometry}

@@

{\bf Our response:} {\color{blue} 
	To address this concern, the following was added on lines XX-XX in the updated manuscript:

@@

{\bf Our response:} {\color{blue} The statements on the lines  17-19 of our initial submission are misleading, as
the referee correctly recognized. We replace them with the following on lines 18-27 of the updated manuscript:

>>>>

~\cite{hofler13,bazarov05,yrss:09,jefferson,gull1,gull2} \documentclass{article}
\usepackage{latexsym}
\usepackage{color}
\setlength{\parskip}{3mm}
\setlength{\parindent}{0pt}
\usepackage[margin=1in]{geometry}

@@

{\bf Our response:} {\color{blue} 
	To address this concern, the following was added on lines 28-41 in the updated manuscript:

@@

{\bf Our response:} {\color{blue} The statements on the lines  17-19 of our initial submission are misleading, as
the referee correctly recognized. We replace them with the following on lines 17-27 of the updated manuscript:

### 2019-01-31 paper/submission/prab.tex
finished adding in Linda's edits

\documentclass[%
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
preprint,
linenumbers,
%twocolumn,
%showpacs,preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
amsmath,amssymb,
aps,
%pra,
%prb,
%rmp,
prstab,
%prstper,
%floatfix,
]{revtex4-1}

\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage{todonotes}
\usepackage{siunitx}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\usepackage{fancyvrb}
\usepackage{booktabs}
%\usepackage{cite}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{url}
%\usepackage{footmisc}
%\usepackage{multicol}
%\usepackage{color}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,snakes,backgrounds}
\usetikzlibrary{mindmap,trees}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{plotmarks}
\usepackage{listings}
\newcounter{lstmain}
\setcounter{lstmain}{1}

\usepackage{graphicx,xcolor,enumitem}
%\usepackage{cuted}
\newcommand{\lsnote}[1]{\textsf{{\color{violet}{ LS note:}   #1 }}}

@@

\usepackage{array}
\newcolumntype{C}{ >{\centering\arraybackslash} m{2.5cm} }
\newcolumntype{D}{ >{\centering\arraybackslash} m{3cm} }

\newcommand{\nrnote}[1]{\textsf{{\color{blue}{ NN note:}   #1 }}}
\newcommand{\lsedit}[1]{\textsf{{\color{violet}{ ls note:}   #1 }}}
\begin{document}

\title{A Parallel General Purpose Multi-Objective Optimization Framework,
  with Application To Electron Beam Dynamics}
%\thanks{A footnote to the article title}%

@@

\begin{abstract}
Particle accelerators are invaluable tools for research in the basic and
  applied sciences, in fields such as materials science, chemistry,
  the biosciences, particle physics, nuclear physics and medicine.
The design, commissioning, and operation of accelerator facilities is a
  non-trivial task, due to the large number of control parameters and the
  complex interplay of several conflicting design goals.
We propose to tackle this problem by means of multi-objective optimization
  algorithms which also facilitate a parallel deployment.
In order to compute solutions in a meaningful time frame, a fast 
  and scalable software framework is required.
In this paper, we
present a general-purpose framework for simulation-based
multi-objective optimization methods that allows the automatic
investigation of optimal sets of machine parameters.
Using evolutionary algorithms as the optimizer and \textsc{OPAL} as the 
  forward solver, validation experiments and 
 results of multi-objective optimization problems in the domain of beam
  dynamics are presented. The high charge beam line at the Argonne Wakefield 
  Accelerator Facility was used as the beam dynamics model. 
  Optimized solutions found by the framework were used to finish the design 
  of a two beam acceleration experiment.

@@

\pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
% Classification Scheme.
%\keywords{Suggested keywords}%Use showkeys class option if keyword
%display desired
\maketitle

@@

Particle accelerators play a significant role in many aspects of science and
  technology.
Fields, such as material science, chemistry, the biosciences, particle
  physics, nuclear physics and medicine depend on reliable and effective
  particle accelerators, both as research but as well as practical tools.
Achieving the required performance in the design, commissioning, and operation
  of accelerator facilities is a complex and versatile problem.

Despite the success of on-line models in some facilities [ref here], 
and various model dependent and model independent tuning and optimization techniques, 
empirical tuning by operators a common method used at many research facilities.
When the beam dynamics is non-linear, as is the case with space charge, 
simple and fast models are applicable only in a very restricted manner. 
When it comes to multi-objective optimization, the situation is even more complicated.
In order to be able to reliably identify optimal configurations of
  accelerators, we solve large multi-objective design optimization
  problems to automate the investigation for an optimal set of tuning parameters.
  This approach has been used in the past [] with much success.
The difference here being the implementation and application to a novel
problem at the Argonne Wakefield Accelerator Facility (AWA).

@@

A modular multi-objective software framework was developed (see
 Fig.~\ref{fig:framenetwork}) where the core functionality of the optimizer is decoupled from
 the ``beam dynamics'' but fully integrated in the OPAL \cite{opal} framework. 
To that end, we use a master/slave mechanism where a master process governs a
 set of slave processes given some computational tasks (beam dynamics simulation) to complete.
This separation allows easy interchange of optimization algorithms, forward
  solvers and optimization problems.
A ``pilot'' coordinates all efforts between the optimization algorithm and the
  beam dynamics task. In the sequel we will also use the notion of ``forward solver'' to indicate the beam dynamics task.
This forms a robust and general framework for massively parallel
  multi-objective optimization.
Currently the framework offers one concrete optimization algorithm, an
  evolutionary algorithm employing a \textsc{NSGA-II} selector \cite{pisa}.
Normally, simulation based approaches are plagued by the trade off between
  level of detail and time to solution.
This problem is addressed later in Section~(\ref{awa:subsection:test}) by using forward solvers with different time and
  resolution complexity.

The framework discussed here, incorporates the following three contributions:
%
\begin{enumerate}
  \item Implementation of a scalable optimization algorithm capable of
        approximating Pareto fronts in high dimensional spaces,
  \item design and implementation of a modular framework that is simple to use
        and deploy on large scale computational resources, and
  \item demonstrating the usefulness of the proposed framework on a real world
        application in the domain of particle accelerators,
        with the optimization problem set as 
        the high charge photoinjector at the Argonne Wakefield Accelerator (AWA). 
\end{enumerate}

The next section introduces the notation of multi-objective optimization
theory and describes the first implemented optimizer.
In Section~\ref{sec:framework} the implementation of the framework is discussed.
We introduce the employed forward-solver in Section~\ref{sec:forward-solver}.
A validation and a proof of concept application in the beam dynamics problems 
mentioned above is discussed in Section~\ref{sec:experiments}.

@@

\begin{figure}
    \centering
    \scalebox{1}{
    \begin{tikzpicture}[scale=0.8, transform shape, text=black]
    \input{figures/ga_explained_big.tex}
    \end{tikzpicture}
	}
  \caption{Schematic view of interplay between selector and variator. The
  selector ranks all individuals in the population according to fitness and
  subsequently the variator uses the fittest individuals to produces new
  offspring. Finally, the new children are reintroduced in the population.}
  \label{fig:varsel}
\end{figure}

@@

The basic assumption in simulation-based optimization is that a
  call to an expensive simulation software component present in the
  constraints or objectives is needed.
The framework is divided in three exchangeable components, as shown in
  Fig.~\ref{fig:opt-framework-layout}, to encapsulate the major behavioral
  patterns of the framework.
%
\begin{figure}
  \centering
  \scalebox{0.85}{
  \begin{tikzpicture}[text=black]
  \input{figures/opt-framework-layout.tex}
  \end{tikzpicture}
}

  \caption{Schematic view of messages passed within the network between the
    three roles.
  The dashed cyan path describes a request (job $j_1$) sent from $O_i$ to the
  \textsc{Pilot} being handled by $W_j$. Subsequently the result $r_k$ is
  returned to the requesting \textsc{Optimizer} ($O_i$). The work $W_j$ are beam dynamics 
  simulation within OPAL.}
  \label{fig:opt-framework-layout}
\end{figure}

@@

The framework contains a wrapper implementing the API mentioned in
  Listing 3 for using \textsc{OPAL} \cite{opal} as the forward solver.
\textsc{OPAL} provides different trackers for cyclotrons and linear
  accelerators with satisfactory parallel performance. % \cite{akir:09}.

@@

\bibliographystyle{abbrv}
\bibliography{paper}

>>>>

\documentclass[preprint,linenumbers,amsmath,amssymb,aps,prstab]{revtex4-1}%

\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{siunitx}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\usepackage{fancyvrb}
%\usepackage{booktabs}
%\usepackage{amsmath}
%\usepackage{amsfonts}
\usepackage{url}
%\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{listings}
\newcounter{lstmain}
\setcounter{lstmain}{1}
\usepackage{graphicx,xcolor,enumitem}
\usepackage{booktabs}

@@

\begin{document}

\title{A Parallel General Purpose Multi-Objective Optimization Framework,
  with Application To Electron Beam Dynamics}

@@

\begin{abstract}
Particle accelerators are invaluable tools for research in the basic and
  applied sciences, such as materials science, chemistry,
  the biosciences, particle physics, nuclear physics and medicine.
The design, commissioning, and operation of accelerator facilities is a
  non-trivial task, due to the large number of control parameters and the
  complex interplay of several conflicting design goals.
We propose to tackle this problem by means of multi-objective optimization
  algorithms which also facilitate a parallel deployment.
In order to compute solutions in a meaningful time frame, a fast 
  and scalable software framework is required.
In this paper, we
present a general-purpose framework for simulation-based
multi-objective optimization methods that allows the automatic
investigation of optimal sets of machine parameters.
Using evolutionary algorithms as the optimizer and \textsc{OPAL} as the 
  forward solver, validation experiments and 
 results of multi-objective optimization problems in the domain of beam
  dynamics are presented. The high charge beam line at the Argonne Wakefield 
  Accelerator Facility was used as the beam dynamics model. 
  Optimized solutions found by the framework were used to finish the design 
  of a two beam acceleration experiment.

@@

\maketitle

@@

Particle accelerators play a significant role in many aspects of science and
  technology.
Fields, such as material science, chemistry, the biosciences, particle
  physics, nuclear physics and medicine depend on reliable and effective
  particle accelerators, both as research and practical tools.
Achieving the required performance in the design, commissioning, and operation
  of accelerator facilities is a complex and versatile problem.
Despite the success of on-line models in some facilities~\cite{xiaobiao}, 
and various model dependent and model independent tuning and optimization techniques, 
empirical tuning by operators is a common method used at many research facilities.
When the beam dynamics is non-linear, as is the case with space charge, 
simple and fast models are applicable only in a very restricted manner. 
When it comes to multi-objective optimization, the situation is even more complicated.
In order to be able to reliably identify optimal configurations of
  accelerators, we solve large multi-objective design optimization
  problems to automate the investigation for an optimal set of tuning parameters.
  This approach has been used in the past with much success~\cite{hofler13,bazarov05,yrss:09,jefferson,gull1,gull2}.
The difference here being the implementation and application to a 
problem at the Argonne Wakefield Accelerator Facility (AWA).

A hallmark of the AWA facility is the flexibility to swap physical
components in the beamlines, which enables different, often novel,
accelerator research experiments to take place.  Not only do the
physical machine components change, the beam characteristics also vary
considerably to meet different needs.  The facility operates at both low
and high charge (up to 100 nC), and at high charge strong nonlinearities
require a full 3D space charge approach in simulations for modeling.  
Finding optics solutions in this regime, especially when
there are additional constraints such as the small aperture two-beam
accelerating structures, is challenging even without the quick
turnaround of the beamline configurations.  Therefore, it has been an
important research objective to develop a precise, e.g. 3D model
embedded into a multi-objective optimization framework that may be used
as a flexible platform for optimization of changing machine
configurations operated at different charge levels. While other codes,
such as GPT~\cite{gpt} and ELEGANT~\cite{elegant}, also have
integrated genetic optimization algorithms; the OPAL~\cite{opal} framework
differentiates itself by being open source (i.e. free to use), massively
parallel, and fully 3D.

@@

A modular multi-objective software framework was developed (see
 Fig.~\ref{fig:framenetwork}) where the core functionality of the optimizer is decoupled from
 the ``beam dynamics'' but fully integrated in the OPAL framework. 
To that end, we use a master/slave mechanism where a master process governs a
 set of slave processes given some computational tasks (beam dynamics simulation) to complete.
This separation allows easy interchange of optimization algorithms, forward
  solvers and optimization problems.
A ``pilot'' coordinates all efforts between the optimization algorithm and the
  beam dynamics task. In the following sections, we will also use the notion of ``forward solver'' to indicate the beam dynamics task.
This forms a robust and general framework for massively parallel
  multi-objective optimization.
Currently the framework offers one concrete optimization algorithm, an
  evolutionary algorithm employing a \textsc{NSGA-II} selector \cite{pisa}.
Normally, simulation based approaches are plagued by the trade off between
  level of detail and time to solution.
This problem is addressed later in Section~(\ref{awa:subsection:test}) by using forward solvers with different time and
  resolution complexity.

The framework discussed here, incorporates the following three contributions:
%
\begin{enumerate}
  \item Implementation of a scalable optimization algorithm capable of
        approximating Pareto fronts in high dimensional spaces,
  \item design and implementation of a modular framework that is simple to use
        and deploy on large scale computational resources, and
  \item demonstration of the usefulness of the proposed framework on a real world
        application in the domain of particle accelerators. This is done
        with the optimization problem set as 
        the high charge photoinjector at the Argonne Wakefield Accelerator (AWA). 
\end{enumerate}

The next section introduces the notation of multi-objective optimization
theory and describes the first implemented optimizer.
In Section~\ref{sec:framework}, the implementation of the framework is discussed.
We introduce the employed forward-solver in Section~\ref{sec:forward-solver}.
A validation and a proof of concept application in the beam dynamics problems 
mentioned above is discussed in Section~\ref{sec:experiments}.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{figures/ga_explained_big}
  \caption{Schematic view of interplay between selector and variator. The
  selector ranks all individuals in the population according to fitness and
  subsequently the variator uses the fittest individuals to produces new
  offspring. Finally, the new children are reintroduced in the population.}
  \label{fig:varsel}
\end{figure}

@@

The basic assumption in simulation-based optimization is that a
  call to an expensive simulation software component present in the
  constraints or objectives is needed.
The framework is divided in three exchangeable components, as shown in
  Fig.~\ref{fig:opt-framework-layout}, to encapsulate the major behavioral
  patterns of the framework.
%
\begin{figure}
  \centering
  \includegraphics[width=0.7\linewidth]{figures/opt-framework-layout}
  \caption{Schematic view of messages passed within the network between the
    three roles.
  The dashed cyan path describes a request (job $j_1$) sent from $O_i$ to the
  \textsc{Pilot} being handled by $W_j$. Subsequently the result $r_k$ is
  returned to the requesting \textsc{Optimizer} ($O_i$). The work $W_j$ are beam dynamics 
  simulation within OPAL.}
  \label{fig:opt-framework-layout}
\end{figure}

@@

The framework contains a wrapper implementing the API mentioned in
  Listing 3 for using \textsc{OPAL} \cite{opal} as the forward solver.
\textsc{OPAL} provides different trackers for cyclotrons and linear
  accelerators with satisfactory parallel performance.

@@

\bibliography{paper}

### 2019-01-31 paper/submission/theor-experiment.tex
finished adding in Linda's edits

\begin{figure}
    \centering
    \begin{tikzpicture}[text=black]
      \input{figures/hypervolume.tex}
    \end{tikzpicture}
  \caption{The hypervolume for a two-objective optimization problem
  corresponds to the shaded area formed by the dashed rectangles spanned by
  all points on the Pareto front and an arbitrary selected origin $p_o$.}
  \label{fig:hypervolume}
\end{figure}

@@

\def \gunheight {25}  %25} %double sided number
\def \quadheight {35}
\def \quadleft {115}  %127} %double sided number
\def \kickerleft {145}  %160} % two sided number
\def \leftarrow{10}
\def \bottomofarrows {29}
\def \topofarrows {34}
\begin{figure*}
	\begin{tikzpicture}[every node/.style={anchor=south west,inner sep=0pt},x=1mm, y=1mm,]   
	\node (fig1) at (0,0)
	{\includegraphics[width=\textwidth]{figures/awa-drawing}};
	\node[fill=white, inner sep=2pt] (txt2) at (0,\gunheight) {\large Gun};
	\node[fill=white, inner sep=2pt] (txt2) at (20,\gunheight) {\large Accelerating Cavities};
	\node[fill=white, inner sep=2pt] (txt2) at (\quadleft-5,\quadheight) {\large Quadrupoles};
	\draw [blue, ->, line width=1] (\quadleft+\leftarrow,\topofarrows) -- (\quadleft+\leftarrow, \bottomofarrows);
	\node[fill=white, inner sep=2pt] (txt2) at (\kickerleft,20) {\large $s_1$};
	\node[fill=white, inner sep=2pt] (txt2) at (\kickerleft+8,20) {\large $s_2$};
	\node[fill=white, inner sep=2pt] (txt2) at (\kickerleft,\quadheight) {\large Kicker};
	\draw [blue, ->, line width=1] (\kickerleft+\leftarrow-3,\topofarrows) -- (\kickerleft+\leftarrow-3, \bottomofarrows);	
	\draw [black, ->, line width=1] (0,-2) -- (100, -2);
	\node[fill=white, inner sep=2pt] (txt2) at (50,0) {\large Beam Direction};
	\end{tikzpicture}
	\caption{Side view of the high charge linac at the AWA. 
		All hardware in this drawing is currently installed. 
	Note locations $s_1$ and $s_2$, before and after the kicker.}
	\label{awa-linac}
	%\vspace{-7em}
\end{figure*}

\def \septheight {65}
\def \bottomarrow {55} %57}
\def \kleft {13}
\def \sleft {38}%41.5}
\def \sheight {45}%47}
\def \beam {35}
\begin{figure*}
	\begin{tikzpicture}[every node/.style={anchor=south west,inner sep=0pt},x=1mm, y=1mm,]   
	\node (fig2) at (0,0)
	{\includegraphics[width=\textwidth]{figures/tba_dogleg}};
	\node[fill=white, inner sep=2pt] (txt2) at (3,\sheight) {\large $s_1$};
	\node[fill=white, inner sep=2pt] (txt2) at (20,\sheight) {\large $s_2$};
	\node[fill=white, inner sep=2pt] (txt2) at (41,40) {\large $s_3$}; %(46,45)
	\node[fill=white, inner sep=2pt] (txt2) at (33,\septheight) {\large Septum};
	\draw [blue, ->, line width=1] (\sleft,\septheight) -- (\sleft, \bottomarrow);	
	\node[fill=white, inner sep=2pt] (txt2) at (7,\septheight) {\large Kicker};
	\draw [blue, ->, line width=1] (\kleft,\septheight) -- (\kleft, \bottomarrow);
	\draw [black, ->, line width=1] (0,\beam) -- (100,\beam);
	\node[fill=white, inner sep=2pt] (txt2) at (50,\beam+2) {\large Beam Direction};
	\end{tikzpicture}
	\vspace{-12em}
	\caption{Continuation of the high charge beam line layout at the AWA, top view. 
		This is the proposed two beam acceleration section. 
		Only the kicker in this drawing is installed. 
	Note $s_3$, the entrance to the fifth quadrupole on the beam line.
	This is the optimization location.}
	\label{awa-tba}
\end{figure*}
%
%\vspace{-1em}

@@

\begin{table}%[h!]
	\begin{center}
		\caption{Checkmarks (\cmark) indicate desired beam parameters are resolved at that time step. 
			An (\xmark) indicates the time step is too large, and results are nonphysical.}
		\label{timestep}
		\begin{tabular*}{0.48\textwidth}{c @{\extracolsep{\fill}} C c D }
			\hline\noalign{\smallskip}
			Time Step (dT) & Linac & Drift & Quadrupoles \\
			\noalign{\smallskip}\hline\noalign{\smallskip}
			$5 \times10^{-10}$  & \xmark & \xmark & \xmark \\
			$1 \times10^{-10}$  & \xmark & \xmark & \xmark \\
			$5 \times10^{-11}$  & \xmark & \xmark & \xmark \\
			$1 \times10^{-11}$  & \cmark & \cmark & \xmark \\
			$5 \times10^{-12}$  & \cmark & \cmark & \xmark \\
			$1 \times10^{-12}$  & \cmark & \cmark & \cmark \\
			\noalign{\smallskip}\hline
		\end{tabular*}
	\end{center}
\end{table}

@@

\subsubsection{Hyper parameter Scan}
While the optimization problem and goals were well defined (Subsection \ref{awaproblem}), 
it was not clear what the best hyper parameters for the genetic algorithm would be.
These parameters include gene mutation probability, mutation probability, 
recombination probability, number of individuals, 
and number of generations to complete. 
Given the beam line in Fig.~\ref{awa-linac},
four small optimization experiments were done with various hyper parameters. 
Similar to the time step scan, 
the goal of this exercise was to determine which set of optimization
parameters strongly influence the results, 
and whether there was a time to solution difference.
From here on, we will reference each experiment as ex-1, ex-2, ex-3, and ex-4
as shown in Table \ref{extable}. 
\begin{table}%[h!]
	\begin{center}
		\caption{Input Parameters for initial twenty four hour AWA optimization experiments. 
			The gene mutation probability was equal to the mutation probability (not shown) in all four experiments. 
			The max number of individuals per generation was~80.}
		\label{extable}
		\begin{tabular*}{0.48\textwidth}{l @{\extracolsep{\fill}}| C | C | D }
			\hline\noalign{\smallskip}
			& Gene Mutation Probability & Recombination Probability & Number of completed generations \\
			\noalign{\smallskip}\hline\noalign{\smallskip}
			ex-1 &  0.1  & 0.9  &  96 \\
			ex-2 &  0.3  & 0.7  &  81 \\
			ex-3 &  0.8  & 0.2  &  53 \\
			ex-4 &  0.01 & 0.09 &  95 \\
			\noalign{\smallskip}\hline
		\end{tabular*}
	\end{center}
\end{table}

@@

The objectives include: $\varepsilon_{x}\left(s = s_1\right)\text{, } \varepsilon_{x}\left(s = s_2\right)$, $\text{rms}_{s}\left(s = s_1\right)\text{, and }  \text{rms}_{s}\left(s = s_2\right)$. 
The OPAL input file for ex-3, and subsequent optimization runs in this paper, can be found at in following repository: 
\url{https://github.com/nneveu/awa-tba}.
%is given as an example to show how optimization and design variables are defined:

@@

\begin{figure}
	\centering
	\begin{minipage}{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{figures/ex-pareto1-paperedit}
		(a) Pareto fronts for ex-1 through ex-4 at $s_1$.
		%\caption{(a) Pareto fronts at $s_1$.}
		%\label{expareto1}
		%\vspace{2em}
	\end{minipage}
	\begin{minipage}{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{figures/ex-pareto2-paperedit}
		(b) Pareto fronts for ex-1 through ex-4 at $s_2$.
		%\caption{(b) Pareto fronts at $s_2$.}
		%\label{expareto2}
	\end{minipage}
	\caption{Comparison of Pareto fronts for initial optimization experiments, ex-1 through ex-4.}
	\label{expareto}
\end{figure}

@@

Equations (\ref{eq:awa:firstconstr}) to
(\ref{eq:awa:lastdvar}) define the charge, gun voltage, linac voltages, 
laser radius, gun phase, and linac cavity phases (in that order). 
These are parameters in the simulation 
that must be defined, but do not vary during the optimization.
%\vspace{-1em}
The AWA 
design variables, objectives, and constraints in the OPAL input file as shown in
the following code: %equations (\ref{eq:awa:p1}) to (\ref{eq:awa:lastdvar}). 
%\vspace{0.2cm}

@@

\begin{figure}
	\includegraphics[width=0.65\textwidth]{figures/xy-max-min-sigma-paper}
	\caption{Optimized beam sizes along high charge beam line. The gun is located at $s=0$, 
	both x and y beam sizes are shown. The black line represents the relevant beam line aperture, while
	the green line indicates the location of the optimization.}
	\label{fig:stat}
\end{figure}
\begin{table}%[h!]
	\begin{center}
		\caption{Input Parameters for the optimized solution shown in Figures~\ref{fig:pareto1} and \ref{fig:stat}.}
		\label{tab:designopt}   
		\begin{tabular}{l|c|c}
			\noalign{\smallskip}\hline\noalign{\smallskip}
			%\rowcolor{blue!30} 
			\textbf{Design Variable} & \textbf{Unit}	&  \textbf{Value}  \\ 
			\noalign{\smallskip}\hline\noalign{\smallskip}
			{Buck Focusing Solenoid} & amps	& 478 \\
			Matching Solenoid &	amps	& 197	  \\
			Quadrupole 1& T-m		& -0.8	\\ 
			Quadrupole 2& T-m		& 0.9	\\
			Quadrupole 3 & T-m		& 0.8	\\
			Quadrupole 4 & T-m		& -1.0	\\ 
			Bunch Length & mm 		& 1.5	\\
			\noalign{\smallskip}\hline\noalign{\smallskip}
		\end{tabular}
	\end{center}
\end{table}

>>>>

\begin{figure}
    \centering
      \includegraphics[width=0.4\linewidth]{figures/hypervolume}
  \caption{The hypervolume for a two-objective optimization problem
  corresponds to the shaded area formed by the dashed rectangles spanned by
  all points on the Pareto front and an arbitrary selected origin $p_o$.}
  \label{fig:hypervolume}
\end{figure}

@@

\begin{figure*}
\includegraphics[width=0.9\linewidth]{figures/awa-drawing}
	\caption{Side view of the high charge linac at the AWA. 
		All hardware in this drawing is currently installed. 
	Note locations $s_1$ and $s_2$, before and after the kicker.}
	\label{awa-linac}
	%\vspace{-7em}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.9\linewidth]{figures/tba_dogleg2}
	\caption{Continuation of the high charge beam line layout at the AWA, top view. 
		This is the proposed two beam acceleration section. 
		Only the kicker in this drawing is installed. 
	Note $s_3$, the entrance to the fifth quadrupole on the beam line.
	This is the optimization location.}
	\label{awa-tba}
\end{figure*}
%
%\vspace{-1em}

@@

\begin{table}%[h!]
	\begin{center}
		\caption{Checkmarks (\cmark) indicate desired beam parameters are resolved at that time step. 
			An (\xmark) indicates the time step is too large, and results are nonphysical.}
		\label{timestep}
		\begin{tabular*}{0.48\textwidth}{cccc}
			\hline\noalign{\smallskip}
			Time Step (dT) & Linac & Drift & Quadrupoles \\
			\noalign{\smallskip}\hline\noalign{\smallskip}
			$5 \times10^{-10}$  & \xmark & \xmark & \xmark \\
			$1 \times10^{-10}$  & \xmark & \xmark & \xmark \\
			$5 \times10^{-11}$  & \xmark & \xmark & \xmark \\
			$1 \times10^{-11}$  & \cmark & \cmark & \xmark \\
			$5 \times10^{-12}$  & \cmark & \cmark & \xmark \\
			$1 \times10^{-12}$  & \cmark & \cmark & \cmark \\
			\noalign{\smallskip}\hline
		\end{tabular*}
	\end{center}
\end{table}

@@

\subsubsection{Hyper parameter Scan}
While the optimization problem and goals were well defined (Subsection \ref{awaproblem}), 
it was not clear what the best hyper parameters for the genetic algorithm would be.
These parameters include gene mutation probability, mutation probability, 
recombination probability, number of individuals, 
and number of generations to complete. 
Given the beam line in Fig.~\ref{awa-linac},
four small optimization experiments were done with various hyper parameters. 
Similar to the time step scan, 
the goal of this exercise was to determine which set of optimization
parameters strongly influence the results, 
and whether there was a time to solution difference.
From here on, we will reference each experiment as ex-1, ex-2, ex-3, and ex-4
as shown in Table \ref{extable}. 
\begin{table}%[h!]
	\begin{center}
		\caption{Input Parameters for initial twenty four hour AWA optimization experiments. 
			The gene mutation probability was equal to the mutation probability (not shown) in all four experiments. 
			The max number of individuals per generation was~80.}
		\label{extable}
		\begin{tabular*}{0.48\textwidth}{l ccc}
			& Gene Mutation Probability & Recombination Probability & Number of completed generations \\
			ex-1 &  0.1  & 0.9  &  96 \\
			ex-2 &  0.3  & 0.7  &  81 \\
			ex-3 &  0.8  & 0.2  &  53 \\
			ex-4 &  0.01 & 0.09 &  95 \\
		\end{tabular*}
	\end{center}
\end{table}

@@

The objectives include: $\varepsilon_{x}\left(s = s_1\right)\text{, } \varepsilon_{x}\left(s = s_2\right)$, $\text{rms}_{s}\left(s = s_1\right)\text{, and }  \text{rms}_{s}\left(s = s_2\right)$. 
The OPAL input file for ex-3, and subsequent optimization runs in this paper, can be found at in following repository: 
\url{https://github.com/nneveu/awa-tba}.

@@

\begin{figure}
	\centering
	\begin{minipage}{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{figures/ex-pareto1-paperedit}
		(a) Pareto fronts for ex-1 through ex-4 at $s_1$.
		%\vspace{2em}
	\end{minipage}
	\begin{minipage}{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{figures/ex-pareto2-paperedit}
		(b) Pareto fronts for ex-1 through ex-4 at $s_2$.
		%\label{expareto2}
	\end{minipage}
	\caption{Comparison of Pareto fronts for initial optimization experiments, ex-1 through ex-4.}
	\label{expareto}
\end{figure}

@@

Equations (\ref{eq:awa:firstconstr}) to
(\ref{eq:awa:lastdvar}) define the charge, gun voltage, linac voltages, 
laser radius, gun phase, and linac cavity phases (in that order). 
These are parameters in the simulation 
that must be defined, but do not vary during the optimization.
The AWA design variables, objectives, and constraints in the OPAL input file as shown in
the repository.
%\vspace{0.2cm}

@@

\begin{figure}
	\includegraphics[width=0.65\textwidth]{figures/xy-max-min-sigma-paper}
	\caption{Optimized beam sizes along high charge beam line. The gun is located at $s=0$, 
	both x and y beam sizes are shown. The black line represents the relevant beam line aperture, while
	the green line indicates the location of the optimization.}
	\label{fig:stat}
\end{figure}
\begin{table}%[h!]
	\begin{center}
		\caption{Input Parameters for the optimized solution shown in Figures~\ref{fig:pareto1} and \ref{fig:stat}.}
		\label{tab:designopt}   
		\begin{tabular}{ccc}
			\toprule
			\textbf{Design Variable} & \textbf{Unit}	&  \textbf{Value}  \\ 
			\midrule
			{Buck Focusing Solenoid} & amps	& 478 \\
			Matching Solenoid &	amps	& 197	  \\
			Quadrupole 1& T-m		& -0.8	\\ 
			Quadrupole 2& T-m		& 0.9	\\
			Quadrupole 3 & T-m		& 0.8	\\
			Quadrupole 4 & T-m		& -1.0	\\ 
			Bunch Length & mm 		& 1.5	\\
			\bottomrule
		\end{tabular}
	\end{center}
\end{table}
